Embracing the Laws of Physics: \\ Three Reversible Models of Computation

### 2018-07-03 survey/survey.tex
actually draw said pentagon diagram. tikzcd is rather nice.

\jc{Say that the bottom line in Fig.~\ref{figj} is actually the
pentagon diagram of monoidal categories. Draw it, and label it
using our combinators instead of the usual ones.}

>>>>

The bottom line in Fig.~\ref{figj} is actually a linear
restatement of the famous ``pentagon diagram'' stating a
particular coherence condition for monoidal categories~\cite{KELLY197197}.
To make the relation between $\Pi$ as a language and the
language of category theory, the figure below
the same morphism but in categorical terms.

\begin{center}
\begin{tikzcd}[column sep=normal]
   & (A \times (B \times C)) \times D \arrow [dr, "\assocrt"] & \\
((A \times B) \times C) \times D \arrow [ur, "\assocrt \otimes \mathit{id}\leftrightarrow"] 
   \arrow [d, "\assocrt"] & 
       & A \times ((B \times C) \times D) \arrow [d, "\mathit{id}\leftrightarrow \otimes \assocrt" ]\\
(A \times B) \times (C \times D) \arrow [rr, "\assocrt"] & & A \times (B \times (C \times D))
\end{tikzcd}
\end{center}
